Summary of the things that I learned

### 2024-09-25 300-univalent-foundations.tex
Add a reference about independence of the univalence axiom

\section{The univalence axiom}
Now, even for a basic category, like the category of types, it seems impossible to prove that the univalence principle holds. However, this is no surprise: it turns out that it is independent of the axioms of Martin-Löf type theory (\TODO \textbf{Is this true? I need a reference for this, but could not find one}). That is: it cannot be proven, but assuming it as an axiom does not yield contradictions.

>>>>

\section{The univalence axiom}
Now, even for a basic category, like the category of types, it seems impossible to prove that the univalence principle holds. However, this is no surprise: It turns out that there is a model in set theory for Martin-Löf type theory with univalence (\autocite{simplicial-set-model}), but also for Martin-Löf type theory with proof irrelevance (\autocite{proof-irrelevant-model}). In the latter, the type $ x = y $ has at most one element for all $ x, y : T $ and all types $ T $, which contradicts univalence. Therefore, univalence is independent of the axioms of Martin-Löf type theory: both univalence or its negation cannot be proved, but either can be assumed as an axiom.

### 2024-09-25 500-previous-work.tex
Add a reference about independence of the univalence axiom

Since Lambek showed an equivalence between simply typed $ \lambda $-calculi and cartesian closed categories, and since we have a construction for an untyped $ \lambda $-calculus from a cartesian closed category with a reflexive object, we can wonder whether this construction constitutes contitutes an equivalence between untyped $ \lambda $-calculi and some class of categories. This question finds a partial answer in the following theorem, originally proven in a very syntactical way by Dana Scott (see \autocite{curry}, page 418).
\begin{theorem}\label{thm:Scott}
  We can obtain every untyped $ \lambda $-calculus as the endomorphism theory of some object in some category.
\end{theorem}
\begin{proof}
  Let $ L $ be a $ \lambda $-theory. Scott considers its category of retracts $ \R $, with `universal object' $ U $.

>>>>

Since Lambek showed an equivalence between simply typed $ \lambda $-calculi and cartesian closed categories, and since we have a construction for an untyped $ \lambda $-calculus from a cartesian closed category with a reflexive object, we can wonder whether this construction constitutes contitutes an equivalence between untyped $ \lambda $-calculi and some class of categories. This question finds a partial answer in the following theorem, originally proved in a very syntactical way by Dana Scott (see \autocite{curry}, page 418).
\begin{theorem}\label{thm:Scott}
  We can obtain every untyped $ \lambda $-calculus as the endomorphism theory of some object in some category.
\end{theorem}
\begin{proof}
  Let $ L $ be a $ \lambda $-theory. Scott considers its category of retracts $ \R $, with `universal object' $ U $.
